Combinatorial Mixture Models for Single Cell Assays

### 2012-03-21 MIMOSA.tex
More revisions to the paper text.
Updated figures for multinomial dirichlet.
Rewriting intro.

Signed-off-by: Greg Finak <gfinak@fhcrc.org>

\title{Mixture Models for Single Cell Assays}
\author[1]{Greg Finak}
\author[1]{\ldots Others \ldots}
\author[1]{Raphael Gottardo}

\affil[1]{Vaccine and Infectious Disease Division, Fred Hutchinson Cancer Research Center (FHCRC), Seattle, WA}
\date{\today}

\begin{document}
\maketitle
\begin{abstract}
Immunological endpoints in vaccine trials are measured through a number of different assays that often provide single--cell measurements of multiple, specific intracellular or cell surface proteins, or mRNA expression levels of genes in single cells from specific cell sub--populations. While these measurements are continuous, they are generally discretized during data analysis. For example, in flow cytometry, individual cells are often classified as either positive or negative for a marker based on a predetermined threshold.  One such assay is the intracellular cytokine staining assay that is used to assess an individual's immune response to a vaccine by measuring the abundance antigen--specific T--cell subpopulations producing different cytokines. Cells are classified as cytokine positive or negative based on some threshold, and the resulting discretized count data is used to test for an increase in cytokine producing cells between a treatment and control sample. ICS assays are generally used to identify ``vaccine responders''. These are individuals whose immune system produces significantly more cytokine positive cells in response to antigen stimulation than at baseline. The rarity of these cell populations makes maximizing the sensitivity and specificity of the assay a primary concern. The typical approach to analysis using Fisher's exact test is problematic for two reasons. It can be overly conservative in detecting true differences for small counts, and the data generally do not meet the assumptions of the test. Specifically, the total cell counts across conditions are generally not fixed since these are generated by independent experiments.  In this paper we present a cohort framework based on an empirical-Bayes mixture of Beta--binomial or Dirichlet--Multinomial distributions, for analyzing count data derived from such thresholded single--cell assays. In general, any single--cell assay in which continuous data can be thresholded to classify individual cells into either ``positive'' or ``negative'' categories with respect to one or more variables and compared across different conditions, is suitable for analysis using our method and the extensions presented herein. Using the ICS assay as a motivating example, our method models cytokine–specific T-cell response across all individuals simultaneously while modelling the stimulated and unstimulated cell counts independently. Using simulations and real--world vaccine trial data, we show that our model increases the sensitivity and specificity for positivity calls in ICS assays compared to Fisher's exact test.
\end{abstract}

\section{Introduction}
Single--cell assays are an important tool in immunology, providing a functional and phenotypic snapshot of the immune system at a given time. These assays typically measure multiple variables simultaneously on individual cells in a homogeneous mixture such as whole blood. These variables are used to classify individual cells in the mixture into more homogeneous sub populations based on phenotypic or functional differences. Such single--cell assays provide a snapshot of immune function at a given time and are used for immune monitoring of disease, vaccine research, and diagnosis of haematological malignancies~\cite{}.

@@

The ICS assay in flow cytometry is just one example of the applications of single--cell technologies to immunology. Single--cell gene expression technologies such as Fluidigm are enabling researchers to measure the expression of 96 genes in 96 single cells from a homogeneous population sorted by flow cytometry\cite{Jang:2011uj}. This technology has been used to identify signatures of immune cell sub--populations that correlate with different types of vaccine~\cite{Flatz:2011jb}.

\section{Materials and Methods}

\subsection{Vaccine Trial ICS Dataset Description}
HVTN054 is a phase 1 (safety and efficacy) trial of an adenoviral vector vaccine in individuals without prior immunity~\cite{Peiperl:2010ej}. The vaccine vector expressed Gag, Pol and Env proteins from multiple HIV clades~\cite{Peiperl:2010ej}. Vaccine was given at two increasing doses, as well as a placebo. T--cell responses to antigens in the vaccine were measured via the ICS assay~\cite{Peiperl:2010ej,Horton:2007tsa}. The cytokines measured were IFNg (Interferon--$\gamma$), IL2 (Interleukin--2), TNFa (Tumor necrosis factor--$\alpha$) and IL4 (Interleukin 4)~\cite{Horton:2007tsa}. The sample size consisted of 20 vaccine and four placebo recipients. Statistical analysis of the original positivity calls is described in the original publication~\cite{Peiperl:2010ej}.

\subsection{Data Import, Preprocessing, and Gating}
The gated ICS assay data was imported into R from the original flowJo workspaces (version 6, TreeStar Inc, Ashland, OR)  using the BioConductor tool, \textit{flowWorkspace} (v 1.1.6) and ncdfFlow (v 1.1.4). Data were preprocessed using the flowJo--defined compensation matrices and data transformations extracted from the workspace file, and gated using methods from the flowCore package (v 1.19.2) to extract counts of cytokine positive and negative T--cells for each sample and stimulation~\cite{Hahne:2009vv}.

\subsection{Statistical Analysis of Responder and Non--responder calls}
Below, we summarize the methods for statistical analysis of responder and non--responder calls in the published trial, as well as the methods compared in this paper.
\subsubsection{Statistical Analysis in the Published Trial}
The methodology for statistical analysis and calling responders and non--responders in the original vaccine trial is described in the original publication~\cite{Peiperl:2010ej}. In general, a participant is called a ``responder'' to an antigen stimulation if, for a given cytokine, the number of cytokine--positive T-cells in the antigen--stimulated sample is significantly greater (for some statistical measure of significance) than the number of cytokine--positive T-cells for the negative control (unstimulated) sample from the same individual. In the original trial, significance was measured via one--sided Fisher's exact test for each participant and cytokine, comparing stimulated against unstimulated samples from that individual. A discrete Bonferroni adjustment for multiple comparisons was applied, and stimulations with an adjusted p--value below $\alpha = 0.00001$ were called positive.

\subsection{Statistical Analysis of Responder and Non--responder Calls for Direct Comparison Against the Bayesian Mixture Model Approach}
Positivity calls for vaccine responders and non--responders depend upon the selection of an appropriate threshold. Therefore, to compare different methods of analysis, comparable thresholds for positivity must be selected for the methods. Our mixture modelling approach is fit within each stimulation, and we make positivity calls based on a false discovery rate calculated across individuals, within each stimulation, whereas the originally published analysis makes multiple testing adjustments within individuals, across cytokines \todo[inline]{IS THIS CORRECT, OR IS IT WITHIN INDIVIDUALS ACROSS STIMULATIONS?}. In order to have comparable response rates, we reanalyzed the ICS data using Fisher's one--sided exact test (as described in the original publication) but made positivity calls based on the false discovery rate computed across individuals within each stimulation.

\subsection{Two Competing Beta--Binomial Models}
Our approach to modelling an individual's response to vaccine using ICS data takes a Bayesian approach. We model all observations (individuals) simultaneously for each combination of cytokine and stimulation (including the unstimulated samples). For a given cytokine, we let $n_s$ be the number of cytokine--positive cells in the stimulated sample, $N_s$ the total number of cells in the stimulated sample, and $n_u, N_u$, the number of cytokine--positive and total number of cells in the unstimulated sample, respectively. Note that usually, $N_u \ne N_s$. The observed count data $\mathbf{y}$ is a matrix of size $4 \times P$, where $P$ is the number of participants. For the $i$'th individual $\mathbf{y}_i = \left<N_{si},n_{si},N_{ui},n_{ui}\right>$, and can be represented as the following contingency table: 
% latex table generated in R 2.14.0 by xtable 1.5-6 package
% Wed Oct 12 09:41:50 2011
\begin{table}[ht]
\centering
\parbox{0.8\linewidth}{
\caption{2 x 2 contingency table of counts for cytokine positive and cytokine negative events between stimulated and unstimulated conditions}\label{tab:twobytwo}
\centering
\begin{tabular}{rrr}

@@

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=4in]{Figures/simulations_all} 
   \caption{Performance of the constrained and unconstrained Beta--binomial mixture model vs Fisher's exact test on simulated data. Data were simulated from a constrained model with hyper--parameters estimated from a real data set of Gag1 stimulated, CD4+, IL2 expressing T--cells on day 28 from the HVTN054 trial. For total cell counts from 10,000 to 150,000, we simulated ten data sets each of 500 observations with a response rate of 40\%. The performance, measured by the AUC (area under the curve), of the constrained and unconstrained Beta--binomial mixture model compared to Fisher's exact test is shown in the first panel, as a function of increasing number of cells. The beta distributions for the estimated and true hyper parameters are shown in the second panel for one simulated data set, with N=150,000 events. The ROC curve for Fisher's exact test and the constrained and unconstrained Beta--binomial model for the same simulation are shown in the third panel. The observed vs expected false discovery rate for Fisher's exact test and the constrained and unconstrained Beta--binomial model are shown in the fourth panel.}
   \label{fig:simulations}
\end{figure}

@@

>>>>

\title{Combinatorial Mixture Models for Single Cell Assays}
\author[1]{Greg Finak}
\author[2]{SC De Rosa}
\author[1]{Raphael Gottardo}

\affil[1]{Vaccine and Infectious Disease Division, Fred Hutchinson Cancer Research Center (FHCRC), Seattle, WA}
\affil[2]{HIV Vaccine Trials Network, Fred Hutchinson Cancer Research Center (FHCRC), Seattle, Wa}
\date{\today}

\begin{document}
\maketitle
\begin{abstract}
Immunological endpoints in vaccine trials are measured through a number of different assays that often provide single--cell measurements of multiple, specific intracellular or cell surface proteins, or mRNA expression levels of genes in single cells from specific cell sub--populations. While these measurements are usually continuous, they are often discretized and analyzed as counts of single cells. For example, in flow cytometry, individual cells are often classified as either positive or negative for a marker based on a predetermined threshold.  One such assay is the intracellular cytokine staining assay that is used to assess an individual's immune response to a vaccine by measuring the abundance antigen--specific T--cell subpopulations producing different cytokines. Cells are classified as cytokine positive or negative and the resulting cell counts are used to identify experimental conditions leading to an increase in cytokine producing cells. ICS assays are generally used to identify ``vaccine responders''. These are individuals whose immune system produces significantly more cytokine positive cells in response to antigen stimulation than at baseline. The rarity of these cell populations makes maximizing the sensitivity and specificity of the assay a primary concern. The standard approach to analyze such data, Fisher's exact test, is problematic for two reasons. It can be overly conservative in detecting true differences for small counts, and the data generally do not meet the assumptions of the test. Specifically, the total cell counts across conditions are generally not fixed since these are generated by independent experiments.  In this paper we present a coherent framework based on mixtures of Beta--binomial or Dirichlet--Multinomial distributions for analyzing count data derived from single--cell assays.  Using the ICS assay as a motivating example, our method models cytokine–specific T-cell response across all individuals simultaneously, sharing information across observations using empirical Bayes methods. The model represents the responder and non-responder observations as separate components in the model, stimulated and unstimulated cell counts are modelled independently. Using simulations and real--world vaccine trial data, we show that our model increases the sensitivity and specificity for positivity calls in ICS assays compared to Fisher's exact test. 
\end{abstract}

\section{Introduction}
Single--cell assays are an important tool in immunology, providing a functional and phenotypic snapshot of the immune system at a given time. These assays typically measure multiple variables simultaneously on individual cells in a homogeneous mixture such as whole blood. These variables are used to classify individual cells in the mixture into more homogeneous sub--populations based on phenotypic or functional differences. Such single--cell assays are used for immune monitoring of disease, vaccine research, and diagnosis of haematological malignancies~\cite{Altman:1996wf,Betts:2006dw,Inokuma:2007tn}.

@@

The ICS assay in flow cytometry is just one example of the applications of single--cell technologies to immunology. Single--cell gene expression technologies such as Fluidigm are enabling researchers to measure the expression of 96 genes in 96 single cells from a homogeneous population sorted by flow cytometry\cite{Jang:2011uj}. This technology has been used to identify signatures of immune cell sub--populations that correlate with different types of vaccine~\cite{Flatz:2011jb}. To date, published analysis of Fluidigm data ignore cells where transcripts are undetected, focusing solely on continuous gene expression measurements. However, the proportion of single cells expressing individual genes also carries information and should be evaluated.

Here we present a combinatorial mixture model framework for the analysis of single--cell assay data in which multivariate measurement are made individual cells. The model is used to contrast two conditions (i.e. treatment and control) and identify observations where a significant differences exists between the treatment and control samples with respect to the proportions of cells expressing  different combinations of proteins, genes, or other measured properties of the cells.

We develop our framework in the context of ICS data. While there is no standard approach to analyzing ICS assay data, Fisher's exact test, as well as more ad--hoc methods, are commonly applied on a per--cytokine basis to identify observations where the number of cytokine producing cells is greater in the stimulated than the control data~\cite{Trigona:2003,Sinclair:2004hs,Horton:2007tsa}. The drawbacks of Fisher's exact test applied to 2 x 2 contingency table data when the assumptions of the test are not met, have been reviewed in the literature~\cite{Proschan:2009ks}. Briefly, for single--cell assay data the assumptions of fixed margins are not met, since the observations for treatment and control conditions arise from independent experiments, thus the p--values from Fisher's exact test are incorrect. More importantly, Fisher's exact test does not share information across observations, resulting in low power when counts are small. The framework developed in this paper addresses these issues explicitly.

\section*{Materials and Methods}

\subsection*{Vaccine Trial ICS Dataset Description}
HVTN054 is a phase 1 (safety and efficacy) trial of an adenoviral vector vaccine in individuals without prior immunity~\cite{Peiperl:2010ej}. The vaccine vector expressed Gag, Pol and Env proteins from multiple HIV clades~\cite{Peiperl:2010ej}. Vaccine was given at two increasing doses, as well as a placebo. T--cell responses to antigens in the vaccine were measured via the ICS assay~\cite{Peiperl:2010ej,Horton:2007tsa}. The cytokines measured were IFNg (Interferon--$\gamma$), IL2 (Interleukin--2), TNFa (Tumor necrosis factor--$\alpha$) and IL4 (Interleukin 4)~\cite{Horton:2007tsa}. The sample size consisted of 20 vaccine and four placebo recipients. Statistical analysis of the original positivity calls is described in the original publication~\cite{Peiperl:2010ej}.

\subsection*{Data Import, Preprocessing, and Gating}
The gated ICS assay data was imported into R from the original flowJo workspaces (version 6, TreeStar Inc, Ashland, OR)  using the BioConductor tool, \textit{flowWorkspace} (v 1.1.6) and ncdfFlow (v 1.1.4). Data were preprocessed using the flowJo--defined compensation matrices and data transformations extracted from the workspace file, and gated using methods from the flowCore package (v 1.19.2) to extract counts of cytokine positive and negative T--cells for each sample and stimulation~\cite{Hahne:2009vv}.

\subsection*{Statistical Analysis of Responder and Non--responder calls}
Below, we summarize the methods for statistical analysis of responder and non--responder calls in the published trial, as well as the methods compared in this paper.
\subsubsection*{Statistical Analysis in the Published Trial}
The methodology for statistical analysis and calling responders and non--responders in the original vaccine trial is described in the original publication~\cite{Peiperl:2010ej}. In general, a participant is called a ``responder'' to an antigen stimulation if, for a given cytokine, the number of cytokine--positive T-cells in the antigen--stimulated sample is significantly greater (for some statistical measure of significance) than the number of cytokine--positive T-cells for the negative control (unstimulated) sample from the same individual. In the original trial, significance was measured via one--sided Fisher's exact test for each participant and cytokine, comparing stimulated against unstimulated samples from that individual. A discrete Bonferroni adjustment for multiple comparisons was applied, and stimulations with an adjusted p--value below $\alpha = 0.00001$ were called positive.

\subsection*{Statistical Analysis of Responder and Non--responder Calls for Direct Comparison Against the Bayesian Mixture Model Approach}
Positivity calls for vaccine responders and non--responders depend upon the selection of an appropriate threshold. Therefore, to compare different methods of analysis, comparable thresholds for positivity must be selected for the methods. Our mixture modelling approach is fit within each stimulation, and we make positivity calls based on a false discovery rate calculated across individuals, within each stimulation, whereas the originally published analysis makes multiple testing adjustments within individuals, across cytokines. In order to have comparable response rates, we reanalyzed the ICS data using Fisher's one--sided exact test (as described in the original publication) but made positivity calls based on the false discovery rate computed across individuals within each stimulation.

\subsection*{Two Competing Beta--Binomial Models}
Our approach to modelling an individual's response to vaccine using ICS data takes a Bayesian approach. We model all observations (individuals) simultaneously for each combination of cytokine and stimulation (including the unstimulated samples). For a given cytokine, we let $n_s$ be the number of cytokine--positive cells in the stimulated sample, $N_s$ the total number of cells in the stimulated sample, and $n_u, N_u$, the number of cytokine--positive and total number of cells in the unstimulated sample, respectively. Note that usually, $N_u \ne N_s$. The observed count data $\mathbf{y}$ is a matrix of size $4 \times P$, where $P$ is the number of participants. For the $i$'th individual $\mathbf{y}_i = \left<N_{si},n_{si},N_{ui},n_{ui}\right>$, and can be represented as the following contingency table: 
% latex table generated in R 2.14.0 by xtable 1.5-6 package
% Wed Oct 12 09:41:50 2011
\begin{table}[ht]
\centering
\parbox{0.8\linewidth}{
\caption{2 x 2 contingency table of counts for cytokine positive and cytokine negative events between stimulated and unstimulated conditions}\label{tab:twobytwo}
\centering
\begin{tabular}{rrr}

@@

\subsection*{Testing Multifunctional Response via the Multinomial-Dirichlet model}
We applied the Multinomial--Dirichlet extension of MIMOSA to the HVTN054 trial data to identify observations with cells expressing polyfunctional cytokine profiles. As a proof of principle we limited the model to the two--component case (Figure~\ref{tab:nesting}), with one component for the null model where we expect no difference between stimulations, and one component for the alternative model where we expect a difference between stimulations. We fit the model to the IL4 and TNFa cytokines for Env3 and Env1 stimulated CD4 T--cells from the day zero and day 28 time points (Figures~\ref{fig:polyfunctionality} and \ref{fig:polyfunctionalityenv1}).

The day 28 stimulations show that the posterior probability of response is generally higher for the multivariate MIMOSA model than for the univariate models, and the day zero stimulation (Figure~\ref{fig:polyfunctionality}) shows that the multivariate model has fewer false positives than the univariate MIMOSA model fit to distinct cytokine combinations. We compared multivariate MIMOSA against Fisher's exact test. Fisher's exact test was used to test whether the number of cells expressing a specific combination of cytokines (i.e TNFa+/IL4-, TNFa+/IL4+, and so forth) was significantly higher in the stimulated samples than in the unstimulated samples.  In this comparison, Fisher's exact test detected only one of the 8 responders detected by the MIMOSA model in the Env3 stimulated, day 28 data, and detected two false positives in the day zero data. Fisher's exact test also failed to identify four of the 12 responders identified by the MIMOSA model in the day 28, Env1 stimulated data.

%The classification of responder and non--responder individuals was compared between the multivariate MIMOSA model, univariate MIMOSA models applied to each cytokine combination, and Fisher's exact test applied to each cytokine combination.

%The multivariate MIMOSA model detected two additional responders than Fisher's exact test at the 1\% FDR level (Table~\ref{tab:MDFisher}, top left). The univariate MIMOSA model applied to each cytokine combination individually also outperformed Fisher's exact test, detecting one more responder for the IL4 and TNFa combination (Table~\ref{tab:MDFisher} bottom right), and two more responders for the TNFa and not IL4 cytokine combination (Table~\ref{tab:MDFisher} bottom left).  In the multivariate case, the two responders detected by MIMOSA that were missed by Fisher's exact test had a  2.4--fold and 2.5--fold increase in the proportion of TNFa+/IL4- cells in the stimulated samples than the unstimulated samples. These are the same two samples detected by the univariate MIMOSA model for TNFa+/IL4- cells, one of which also exhibits a 1.7--fold increase in IL4+/TNFa- expression between stimulated and unstimulated samples that was detected by univariate MIMOSA, but not detected by Fisher's exact test.
%\begin{table}[ht]
%\begin{center}
%\begin{minipage}{0.9\linewidth}
%\caption{Confusion matrices comparing responders and non--responders identified by the MIMOSA models and Fisher's exact test. Top left: Fisher's exact test vs the multivariate MIMOSA model for any combination of cytokines.Top right: Fisher's exact test vs MIMOSA for the univariate combination of IL4 and not TNFa. Bottom left: Fisher's exact test vs univariate MIMOSA for TNFa and not IL4. Bottom right: Fisher's exact test vs univariate MIMOSA for IL4 and TNFa. False discovery rate thresholds were set at 1\% for each cytokine combination (except in the multivariate model, where it was 1\% for each observation). }\label{tab:MDFisher}
%\end{minipage}
%\begin{minipage}{0.49\linewidth}
%\center
%\begin{tabular}{rrr}
%  \hline
%  \multicolumn{3}{c}{Any Combination}\\
%  \hline
%&\multicolumn{2}{c}{MIMOSA}\\
%\cmidrule(r){2-3}
% & NR & R \\ 
%\cmidrule(r){1-1}
%Fisher's Exact Test&&\\
%  \hline
%NR &  32 &   2 \\ 
%  R &   0 &   4 \\ 
%   \hline
%\end{tabular}
%\end{minipage}
%\begin{minipage}{0.49\linewidth}
%\center
%\begin{tabular}{rrr}
%\hline
%\multicolumn{3}{c}{IL4 and not TNFa}\\
%  \hline
%&\multicolumn{2}{c}{MIMOSA}\\
%\cmidrule(r){2-3}
% & NR & R \\ 
%\cmidrule(r){1-1}
%Fisher's Exact Test&&\\
%  \hline
%NR &  38 &   0 \\ 
%  R &   0 &   0 \\ 
%   \hline
%\end{tabular}
%\end{minipage}
%\begin{minipage}{0.49\linewidth}
%\center
%\begin{tabular}{rrr}
%  \hline
%  \multicolumn{3}{c}{TNFa and not IL4}\\
%  \hline
%&\multicolumn{2}{c}{MIMOSA}\\
%\cmidrule(r){2-3}
% & NR & R \\ 
%\cmidrule(r){1-1}
%Fisher's Exact Test&&\\
%  \hline
%NR &  36 &   2 \\ 
%  R &   0 &   0 \\ 
%   \hline
%\end{tabular}
%\end{minipage}
%\begin{minipage}{0.49\linewidth}
%\center
%\begin{tabular}{rrr}
%  \hline
%  \multicolumn{3}{c}{IL4 and TNFa}\\
%  \hline
%&\multicolumn{2}{c}{MIMOSA}\\
%\cmidrule(r){2-3}
% & NR & R \\ 
%\cmidrule(r){1-1}
%Fisher's Exact Test&&\\
%  \hline
%NR &  33 &   1 \\ 
%  R &   0 &   4 \\ 
%   \hline
%\end{tabular}
%\end{minipage}
%\end{center}
%\end{table}
\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=4in]{Figures/simulations_all} 
   \caption{Performance of the constrained and unconstrained Beta--binomial mixture model vs Fisher's exact test on simulated data. Data were simulated from a constrained model with hyper--parameters estimated from a real data set of Gag1 stimulated, CD4+, IL2 expressing T--cells on day 28 from the HVTN054 trial. For total cell counts from 10,000 to 150,000, we simulated ten data sets each of 500 observations with a response rate of 40\%. The performance, measured by the AUC (area under the curve), of the constrained and unconstrained Beta--binomial mixture model compared to Fisher's exact test is shown in the first panel, as a function of increasing number of cells. The beta distributions for the estimated and true hyper parameters are shown in the second panel for one simulated data set, with N=150,000 events. The ROC curve for Fisher's exact test and the constrained and unconstrained Beta--binomial model for the same simulation are shown in the third panel. The observed vs expected false discovery rate for Fisher's exact test and the constrained and unconstrained Beta--binomial model are shown in the fourth panel.}
   \label{fig:simulations}
\end{figure}

@@

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=6in]{Figures/Polyfunctionality_ggplot2} 
   \caption{Posterior probabilities from the four--dimensional, Multivariate--Dirichlet, MIMOSA model, compared against posterior probabilities from univariate MIMOSA for each combination of the cytokines IL4 and TNFa, on days zero and 28 for Env--2 peptide stimulated CD4+ T--cells.}
   \label{fig:polyfunctionality}
\end{figure}

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=6in]{Figures/Polyfunctionality_Env1} 
   \caption{Posterior probabilities from the four--dimensional, Multivariate--Dirichlet, MIMOSA model, compared against posterior probabilities from univariate MIMOSA for each combination of the cytokines IL4 and TNFa, on days zero and 28 for Env--1 peptide stimulated CD4+ T--cells.}
   \label{fig:polyfunctionalityenv1}
\end{figure}
